I plan to implement a minimal subset of the
OpenCL specification. This will allow
basic programs using OpenCL to run on the PS3.
I will implement the required functions for
the setup and execution of tasks. This process
involves seven key steps which can be seen in
Appendix D of the OpenCL specification~\cite{opencl}.
\begin{enumerate}
\item Create an OpenCL context
\item Create a command-queue
\item Allocate memory objects
\item Create kernel
  \begin{enumerate}
    \item Create program
    \item Build program
    \item Get kernel
  \end{enumerate}
\item Set work-item dimensions
\item Execute kernel
\end{enumerate}

The three most important steps will 
be the most difficult to implement: creating contexts,
allocating memory objects, and creating kernels.
A context is a data structure that holds all information associated with a
device such as command-queues, memory objects,
and kernels. Allocating memory objects will
be difficult because I must conform to
the OpenCL memory model. Creating kernels
is actually several steps and possibly involves compiling
source code from within an executable. 

\subsection{Deliverables and Milestones}
To achieve this, I will create header and source files which
implement the OpenCL functions using the Cell SDK.
I will also write a short program which uses the
implemented functions. The program will compute
the integral of a simple polynomial using a
Reimann sum. This computation is easily parallelized
and I will be using code from a previous project.

There will be several key milestones in the project.
Note that this is not necessarily the order in which they will be completed.
However, the first milestone will be completed first because
all other milestones rely on it.
\begin{enumerate}
  \item Define the data structures passed 
    between the various functions. 
  \item Implement the context related functions
  \item Implement the memory object related functions
  \item Implement the kernel related functions
  \item Implement the remaining required OpenCL functions
\end{enumerate}

Because of the limited amount of time allocated
for this project, certain functions may be nothing
more than dirty hacks. This will be avoided whenever
possible, but the final deliverable may require them
to function.

\begin{comment}
The ultimate goal is to fully support OpenCL on the PS3. 
However, this may not be possible in the limited
5 week time frame.
\end{comment}
